Object-Oriented Internet - Azure Interoperability

### 2020-12-02 Latex/Manuscript.tex
Revert formatting to default #46
Update Implemetnation
> The PubSub uses JSON and binary Data Transfer Object encodings.

Does it use JSON? I'm seeing that OPC UA defines such encoding [here](https://reference.opcfoundation.org/v104/Core/docs/Part14/7.2.3/) but is the library supporting them? Assuming we are talking in the _implementation_ context.

I've cut `Devices.Provisioning.Transport.*` list point to save on space. I don't know if it's "legal".

\documentclass{jacsart}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{stfloats}
\usepackage{url}
\usepackage{authblk}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{txfonts}
\usepackage[textsize=tiny]{todonotes}

@@

\title{Object-Oriented Internet - Azure Interoperability}
% \title{Object-Oriented Internet - reactive visualization of asynchronous data using AZURE}
\headtitle{OOI - Azure Interoperability}

\author{Mariusz Postół\inst{1}, Piotr Szymczak\inst{1}}
\headauthor{Postół M, Szymczak P, Vasters C}
\affiliation
{
 \inst{1}Lodz University of Technology\\
 Institute of Information Technology\\
 ul. Wólczańska 215, 90-924 Lodz, Poland\\
 mailto:mariusz.postol@p.lodz.pl
}

@@

In the final deployment architecture (Fig. \ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} role has been realized by the \textit{PartDataManagementSetup} that is derived from \textit{DataManagementSetup} provided by the library. \textit{Networking} (SDK) was removed from this diagram for the sake of simplicity. Instantiating \textit{PartDataManagementSetup} is the first step for bootstrapping process of the \textit{Consumer} role functionality. This class provides an entry point to initialize all properties, which are injection points of all parts composing this role. It extents functionality of the \textit{DataManagementSetup} based on the following associated classes:

@@

The encoded JSON messages must be transferred over the network to Azure using the selected protocol stack. The Azure supports the HTTP, AMQP, MQTT (Sec. \ref*{azure-main-technology-features}). All the mentioned protocols are standard ones. Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity. In this case, all parameters required to establish semantic and security contexts are up to the gateway responsibility. Alternatively, the API offered by the dedicated frameworks (libraries) may be used. Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features. In the proposed gateway implementation the Azure interconnection has been obtained using the following \textit{Microsoft.Azure} packages:

\begin{itemize}
      \item \textit{Devices} - Service SDK for Azure IoT Devices
      \item \textit{Devices.Client} - Device SDK for Azure \textit{IoT\ Hub} including dependencies implementing MQTT and AMQP communication
      \item \textit{Devices.Shared} - Common code for Azure IoT Device and Service SDK
      \item \textit{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
      \item \textit{Devices.Provisioning.Transport.Amqp} - Provisioning Device Client AMQP Transport for Azure IoT Devices
      \item \textit{Devices.Provisioning.Transport.Http} - Provisioning Device Client HTTP Transport for Azure IoT Devices
      \item \textit{Devices.Provisioning.Transport.Mqtt} - Provisioning Device Client MQTT Transport for Azure IoT Devices
\end{itemize}

>>>>

\documentclass{article}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{stfloats}
\usepackage{url}
\usepackage{authblk}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{txfonts}
\usepackage[textsize=tiny]{todonotes}

@@

\title{Object-Oriented Internet - Azure Interoperability}
%\\headtitle{OOI - Azure Interoperability}

\author[1]{Mariusz Postół, Piotr Szymczak}
%\author[2]{Piotr Szymczak}
%\headauthor{Postół M, Szymczak P}
\affil[1]
{
 Lodz University of Technology\\
 Institute of Information Technology\\
 ul. Wólczańska 215, 90-924 Lodz, Poland\\
 mailto:mariusz.postol@p.lodz.pl
}
\date{}

@@

In the final deployment architecture (Fig. \ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} role has been realized by the \textit{PartDataManagementSetup} that is derived from \textit{DataManagementSetup} provided by the library. \textit{Networking} (SDK) was removed from this diagram for the sake of simplicity. Instantiating \textit{PartDataManagementSetup} is the first step for bootstrapping process of the \textit{Consumer} role functionality. This class provides an entry point to initialize all properties, which are injection points of all parts composing this role. It extends functionality of the \textit{DataManagementSetup} based on the following associated classes:

@@

The encoded JSON messages must be transferred over the network to Azure using the selected protocol stack. The Azure supports HTTP, AMQP and MQTT protocols (Sec. \ref*{azure-main-technology-features})which are all standard ones. Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity. In this case, all parameters required to establish semantic and security contexts are up to the gateway responsibility. Alternatively, the API offered by the dedicated frameworks (libraries) may be used. Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features. In the proposed gateway implementation the Azure interconnection has been obtained using the following \textit{Microsoft.Azure} packages:

\begin{itemize}
      \item \textit{Devices} - Service SDK for Azure IoT Devices
      \item \textit{Devices.Client} - Device SDK for Azure \textit{IoT\ Hub} including dependencies implementing MQTT and AMQP communication
      \item \textit{Devices.Shared} - Common code for Azure IoT Device and Service SDK
      \item \textit{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
      \item \textit{Devices.Provisioning.Transport.*} - Provisioning Device Client Transports (HTTPS, AMQP, MQTT) for Azure IoT Devices
\end{itemize}
